---
title: "Exploration of German Skills matrices"
output: html_notebook
---

Quick initial exploration of main characteristics from the German skills matrices. The dataset used in this case is the 'occ_SUF.DTA', a 3-digit occupation matrix. 

Reading the data into a network object:
```{r}
library(foreign)
library(igraph)

# read data
data_occ_SUF <- data.frame(read.dta("data/MR_04-17_EN_data/occ_SUF.DTA"))

# select edges where the flow is higher than random
data_occ_SUF_matrix <- data_occ_SUF[data_occ_SUF$SRt>0,]

#build the graph
occ_SUF_net <- graph_from_data_frame(data_occ_SUF_matrix)
```

```{r}
# network object
occ_SUF_net

```

```{r}
V(occ_SUF_net)       # The vertices of the "occ_SUF_net" object

```
## Network visualisation

This is a large network, dificult to visualise. More work (and a better library) must be used to get anything out of the visualsation. 
```{r}
plot(occ_SUF_net, edge.arrow.size=.02, edge.curved=0,

     vertex.color="orange", vertex.frame.color="#555555",

     vertex.label.color="black",

     vertex.label=NA,vertex.size=10.2)

```
## Network and node descriptives

 The proportion of present edges from all possible edges in the network.

```{r}
edge_density(occ_SUF_net, loops=F)
```
The proportion of reciprocated ties.

```{r}
reciprocity(occ_SUF_net)
```
Trasitivity:
  * global - ratio of triangles (direction disregarded) to connected triples.
  * local - ratio of triangles to connected triples each vertex is part of.
```{r}
transitivity(occ_SUF_net, type="global")  # net is treated as an undirected network

transitivity(as.undirected(occ_SUF_net, mode="collapse")) # same as above

transitivity(occ_SUF_net, type="local")

triad_census(occ_SUF_net) # for directed networks 
```

Diameter (length of the shortest path between two nodes) in the network, get_diameter() returns the nodes along the first found path of that distance.

```{r}
diameter(occ_SUF_net, directed=F, weights=NA)

get_diameter(occ_SUF_net, directed=F, weights=NA) 

```

Node degrees:
```{r}
deg <- degree(occ_SUF_net, mode="all")

hist(deg,  main="Histogram of node degree")

```

Degree distribution

```{r}
deg.dist <- degree_distribution(occ_SUF_net, cumulative=T, mode="all")

plot( x=0:max(deg), y=1-deg.dist, pch=19, cex=1.2, col="orange",  xlab="Degree", ylab="Cumulative Frequency")
```

```{r}
degree(occ_SUF_net, mode="in")

centr_degree(occ_SUF_net, mode="in", normalized=T)
```

Closeness (centrality based on distance to others in the graph)
Inverse of the node’s average geodesic distance to others in the network.

```{r}
closeness(occ_SUF_net, mode="all", weights=NA) 

centr_clo(occ_SUF_net, mode="all", normalized=T) 
```
Eigenvector (centrality proportional to the sum of connection centralities)
Values of the first eigenvector of the graph matrix.

```{r}
eigen_centrality(occ_SUF_net, directed=T, weights=NA)

centr_eigen(occ_SUF_net, directed=T, normalized=T) 

```
Betweenness (centrality based on a broker position connecting others)
Number of geodesics that pass through the node or the edge.

```{r}
betweenness(occ_SUF_net, directed=T, weights=NA)

edge_betweenness(occ_SUF_net, directed=T, weights=NA)

centr_betw(occ_SUF_net, directed=T, normalized=T)
```

Average path length: the mean of the shortest distance between each pair of nodes in the network (in both directions for directed graphs).

```{r}
mean_distance(occ_SUF_net, directed=F)
```


